### 2011-06-01 docs/pubs/EIM-2011/framework.tex
a few more notes about SMS API

\subsection{Semantic mediation API}
The SMS API includes ontology management features, annotation manipulation capabilities, and simple concept navigation and visualization widgets. OWL API primarily underlies the ontology management interface providing the RDF/OWL parsing and serialization as well as simple class and property exploration. The Pellet reasoner exposes inferred axioms and relationships that are not explicitly defined in the source ontologies. Inference is particularly powerful when utilizing OBOE Measurement 'templates' that express exactly what (Entity and Characteristic) can be observed and how (Standard and Protocol). 
Annotations are ultimately managed and stored in an opaque local relational database for scalible persistence and query performance; the overhead of in-memory Annotation exploration having proven to be prohibitively limiting for large sets of metadata.

>>>>

\subsection{Semantic mediation API}
The SMS API includes ontology management features, annotation manipulation capabilities, and simple concept navigation and visualization widgets. The API is intended to be a centralized toolkit for use in multiple contexts - be they client or server - that abstracts the specifics of any single semantic library. That being said, OWL API primarily underlies the ontology management interface providing RDF/OWL parsing and serialization as well as simple class and property exploration. A Pellet reasoner exposes inferred axioms and relationships that are not explicitly defined in the source ontologies. Inference is particularly powerful when utilizing OBOE Measurement 'templates' that express exactly what (Entity and Characteristic) can be observed and how (Standard and Protocol).

Annotations are ultimately managed and stored in an opaque local relational database chosen for scalible persistence and query performance; the overhead of in-memory Annotation queries having proven to be prohibitively limiting for large sets of data.
